Overview

### 2020-11-10 README.Rmd
Correcting bib; update README also

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/chainsawriot/oolong.svg?branch=master)](https://travis-ci.org/chainsawriot/oolong)
[![Codecov test coverage](https://codecov.io/gh/chainsawriot/oolong/branch/master/graph/badge.svg)](https://codecov.io/gh/chainsawriot/oolong?branch=master)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/chainsawriot/oolong.svg?branch=master)](https://travis-ci.org/chainsawriot/oolong)
[![Codecov test coverage](https://codecov.io/gh/chainsawriot/oolong/branch/master/graph/badge.svg)](https://codecov.io/gh/chainsawriot/oolong?branch=master)
[![joss stataus](https://joss.theoj.org/papers/6e535564e7142d705f4f3d68b18dac62/status.svg)](https://joss.theoj.org/papers/6e535564e7142d705f4f3d68b18dac62)
[![zenodo](https://zenodo.org/badge/224468858.svg)](https://zenodo.org/badge/latestdoi/224468858)
<!-- badges: end -->
